CONEM2024-0025\\ NEW ABC MULTICRITERIA CLASSIFICATION WITH ANALYTICAL HIERARCHY PROCESS: HOW TO ATTRIBUTE WEIGHTS AND FORCE CONSISTENCY OF PAIRWISE COMPARISONS MATRIX

### 2024-03-13 accepted/CONEM2024/FCPCOM/CONEM2024.tex
updating

@@

    To test the methodology proposed in this article, data were collected for constriction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp). To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing. Based on the data collected, three benchmarks were developed. The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/.

@@

The Tab. 2 presents a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and lead time billing. Appendice A presents the file AHP\_Solution.txt, that presents the results found by the module 'COPSolver: library for solving the multicriteria classification problem' - the results generated from the new ABC multicriteria classification with Analitic Hierarch Process and compare it to the ABC classifications of each criterion, for the items ordered in descending order according to the ABC multicriteria classification.

Based on the results presented in these tables, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto rule. However, when we use the lead time add-on billing criterion, it is possible to verify that the values are close to what is expected. It is also possible to verify in a very clear way that the approach used to measure the weights of the products produces much more relevant results than the simple random assignment of weights. This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible official, assigning the appropriate relevance of the different products, as well as the criteria analyzed.

@@

\begin{table}[h!]
\begin{center}
\begin{tabular}[c]{c r r r}
\multicolumn{4}{c}{new ABC Multcriteria Classification with AHP} \\
\\
\multicolumn{4}{l}{car mechanics company} \\
\cline {1-4} \\
\multicolumn{4}{c}{75 sales between October 2020 and July 2023} \\
\\
  &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\
A &  10 & 23.81 \% &  80 \% \\
B &  15 & 35.71 \% &  95 \% \\
C &  17 & 40.48 \% & 100 \% \\
\cline {1-4} \\
\multicolumn{4}{l}{furniture trades company} \\
\cline {1-4} \\
\multicolumn{4}{c}{254 sales between } \\
\\
 &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\

A &  59 & 23.23 \% &  79.78 \%  \\
B &  56 & 22.05 \% &  94.81 \% \\
C & 139 & 54.72 \% & 100.00 \% \\
\cline {1-4} \\

 \multicolumn{4}{l}{plastic packaging manufacturing company}\\
\cline {1-4} \\
\multicolumn{4}{c}{5,967 sales between November 2019 and February 2023} \\
\\
 &  \multicolumn{1}{c}{quant.} & \multicolumn{1}{c}{\%} & \multicolumn{1}{c}{cutoff} \\

A &   128 &  5.49 \% & \\
B &   726 & 31.12 \% & \\
C & 1,479 & 63.39 \% & \\
\cline {1-4} \\

\end{tabular}
\caption{ABC multicriteria classifications for three companies (results found by COPSolver)}
\label{tab:results}
\end{center}
\end{table}

	\section{DISCUSSION AND FINAL REMARKS}

@@

@@

    \section{RESPONSABILIDADE AUTORAIS}

        Os autores são os únicos responsávelis pelo conteúdo deste trabalho.

        \begin{appendices}
		\setcounter{section}{0}
		\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
		\makeatletter
		\addtocontents{toc}{%
		\begingroup
		\let\protect\l@section\protect\l@subsection
}

>>>>

\usepackage{pdfpages}

\usepackage{graphicx}

@@

    To test the methodology proposed in this article, data were collected for constriction of the pairwise comparison matrix and for ABC classification, using the billing (bl) criterion and other criteria suggested by \cite{FloresWhybark1986}: lead-time (lt); criticality (cr); obsolescence (ob); commonality (cm); substitutability (sb); and repairability (rp). To collect the data, we partnered with three companies from three different sectors: car mechanics; furniture trades; and plastic packaging manufacturing. Based on the data collected, three benchmarks were developed. The date.txt files corresponding to these three benchmarks are available at https://tbfraga.github.io/COPSolver/ benchmarks/. Appendice A presents the data.txt file elaborated with the data provided by the furniture trades company.

@@

Figure \ref{fig:results} presents part of a comparison of the results obtained for the data described above, by ABC classification for the criteria billing and the new ABC multicriteria with Analytic Hierarch Process. Appendice A shows the file AHP\_Solution.txt, that presents the complete results found by the module 'COPSolver: library for solving the multicriteria classification problem'.

\begin{figure}[ht]
	\includegraphics[width=\linewidth]{files/0001.jpg}
  	\caption{Comparison between the ABC classification for the billing criterion and the ABC multicriteria classification}
  	\label{fig:results}
\end{figure}

Based on the results found by COPSolver, we can verify that the ABC classification, considering only the billing criterion, does not follow the normal pattern defined by the Pareto's rule. However, when we use the new ABC multicriteria classification, it is possible to verify that the values are close to what is expected. It is also possible to verify in a very clear way that the approach used to measure the weights of the products produces much more relevant results than the simple random assignment of weights. This approach reduces the viez effect caused by the imbalance of weights and makes the final result carry important qualitative information provided by the responsible official, assigning the appropriate relevance of the different products, as well as the criteria analyzed.

@@

	\section{CONCLUSIONS AND FURTHER WORK}

    In this article we present a new methodology for multicriteria ABC classification as an analytical hierarchy process which includes a procedure to force the consitences of the pairwise comparison matrices, as well as a procedure for assigning weights to the products evaluated according to qualitative criteria and a new equation for calculating the weights of the products in the multicriteria classification. This methodology was tested using data provided by three companies, from three different sectors. As a result, we verified the importance and efficiency of the method developed to force the consistency of the Matrix. We also verified that the new methodology proposed for multicriteria ABC classification generated very coherent results, giving the appropriate importance to the products, according to all the evaluated criteria.

The methodologies developed and results found will be used as a basis for building a portfolio with the identification of product demand pattern and, subsequently, for the development of a combined methodology for demand forecasting. These will be the next works that we will be developing.

@@

    \section{COPYRIGHT LIABILITY}

        The authors are uniquely responsible for the content of this work.

@@

        \newpage
        \begin{appendices}
		\setcounter{section}{0}
		\addtocontents{toc}{\protect\setcounter{tocdepth}{1}}
		\makeatletter
		\addtocontents{toc}{%
		\begingroup
		\let\protect\l@section\protect\l@subsection
}
	\section{data.txt}

	\verbatiminput{files/data.txt}
